|

### 2023-01-19 paper/paper.Rmd
fig 5 modified

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center in the positive direction of bill depth produces regions that have no Gentoo. The two models have similar boundaries except that the RF is more of a step function.}
\label{slice1p}
\end{figure*}

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.95\textwidth]{figures/slice1_p.pdf}}
%\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
%\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center allows for exploring the boundary in different subspaces. Here the center has been shifted out along the axis of bill depth (icon display at right represents slice center position). This region has no Gentoo. The two models have similar boundaries except that the RF is has a step shift in the middle.}
\label{slice1p}
\end{figure*}
